\chapter{Conclusion}
\label{cha:conclusion}

In today's world social platforms are build in a closed proprietary manner. It has been observed that users are communicating with each other in a peer to peer fashion but their all information is routed via central servers, managed by the dedicated organizations. The information of user such as messages, pictures and personal details are shared among these central authorities which results in a data privacy issues. In order to remove this centralization we came up with the idea of decentralized communication, so no one can monitor your data and conversations. In this report, we developed "Decentralized marketplace" where developers can publish decentralized applications/API's and users can download and install them on their own server. Running decentralized application means that you are communicating with your peers directly without involvement of any third party as your entire data is hosted on your own server or device or somewhere in the cloud, which no body can see it. We have covered the topics including the concept, design, implementation and the evaluation of Decentralized marketplace. The development of marketplace is done using the emerging technology of decentralization named blockchain. Blockchain technology provides several advantages for registration of names or other identifiers, such as immutability, trust through distributed consensus, or extensive automated verification via smart contracts. Behind all the functionalities listed above further enhancements can be done on this project. The transfer of entity ownership, recommendation of application and API's, payment systems integration and review system for application and API's in order to filter out the most popular and irrelevant content from the decentralized marketplace. Currently all these things are performed by central autorities who controls the centralized marketplace such as Google play store and Apple app store. In our opinion, the decentralized marketplace will encourage the developers to publish new decentralized applications which will transfer the future towards more decentralization.
